### 2022-10-01 Papers/ICCC-2023/sections/implementation.tex
fixed errors

The final piece of a CTFE First compiler is the Backend Interface.
It is a program, written in the target language, and ran at compile-time that translates the semantic model into the backends assembly language.
Backend Interface implemented for C-=-1 is relativley small and has been described in chapter \ref{implementation/backend-interface}.

@@

The most prymitive types within the hierarchy are \lstinline{StringValue} and \lstinline{IntegerValue}.
They are simple wrappers for strings and integers, present in the host language.
Floating point numbers were not implemented as they were not nessecary for implementation of a basic compiler.

@@

A major motivation in creating CTFE First was the ability to support languages with compile-time metaprogramming.
This includes reflection and modification of the code being compiled.
User program had to be represented as a complete and modifiable object, using the interpreters data structures.

@@

The C-=-1 backend interface utylises LLVM code generation API that has been exposed by the compiler.
The functionality which has been made available to C-=-1 represents a minimal subset of LLVM, that is sufficent to implementing a basic compiler.

@@

Listing \ref{impl:theoretical_llvmir} contains a simple function written in C-=-1, its ideal LLVMIR and LLVMIR generated by C-=-1 compiler.
The current implementation generates a function for each operator, regardless of whether it was defined by the programmer or is a prymitive operation.
They are merely a wrapper around the actual LLVM intrinsic, meant to simplify implementation of the Backend Interface.
Future versions, with additional effort, may generate the ideal LLVMIR from listing \ref{impl:theoretical_llvmir}.

@@

Certain other intrinsic operations were defined using external dependencies.
C-=-1 memory managment library, in the runtime context, builds on a simple interface capable of allocating and deleting a continous buffer.
It is comprised of two functions: \lstinline{unsafe_new} and \lstinline{delete}.

>>>>

The final part of a CTFE First compiler is the Backend Interface.
It is a program, written in the target language, and ran at compile-time that translates the semantic model into the backends assembly language.
Backend Interface implemented for C-=-1 is relativley small and is described in chapter \ref{implementation/backend-interface}.

@@

The most primitive types within the hierarchy are \lstinline{StringValue} and \lstinline{IntegerValue}.
They are simple wrappers for strings and integers, present in the host language.
Floating point numbers were not implemented as they were not nessecary for implementation of a basic compiler.

@@

A major motivation in creating CTFE First was the ability to support languages with compile-time metaprogramming.
This includes reflection and modification of the code being compiled.
User program has to be represented as a complete and modifiable object, using the interpreters data structures.

@@

The C-=-1 backend interface utylises LLVM \cite{llvmir} code generation API that has been exposed by the compiler.
The functionality which has been made available to C-=-1 represents a minimal subset of LLVM, that is sufficent to implementing a basic compiler.

@@

Listing \ref{impl:theoretical_llvmir} contains a simple function written in C-=-1, its ideal LLVMIR and LLVMIR generated by C-=-1 compiler.
The current implementation generates a function for each operator, regardless of whether it was defined by the programmer or is a prymitive operation.
They are merely a wrapper around the actual LLVM intrinsic, meant to simplify implementation of the Backend Interface.
Future versions, with additional effort, may generate the ideal LLVMIR from Listing \ref{impl:theoretical_llvmir}.

@@

Certain other intrinsic operations were defined using external dependencies.
C-=-1 memory managment library, in the runtime context, builds on a simple interface capable of allocating and deleting a continous buffer.
It is comprised of two functions: \lstinline{unsafe_new} and \lstinline{delete}.
In the standard library, they are explicitly mapped to \lstinline{malloc} and \lstinline{free} functions from the C runtime.
